The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-23 paper/sections/methods.tex
Added raycasting and initial patch test figure
working on blending function section

All that remains for the deformation map is to compute blending weights. Our choice of the weighting function is guided by the simple idea that that for a given material point its weight should be highest to whichever surfaces it is closest. This idea lends itself to a simple distance-based weighting method. The first step in this process is to compute \textit{distance weights}. For a given point $\mathbf{X}$ and a set of $n$ we wish to compute a set of distance weights to each surface $\mathbf{\theta}(\mathbf{X}) = \left(\theta_1, \dots, \theta_i, \dots, \theta_n \right)$.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{example-image-a}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}

>>>>

Our kinematic map~\refeq{kinematics} requires blending weights in order to homogenize our per-part representation. 
Specifying weights manually would be antithetical to our goal of providing a seamless translation from surface representation to simulation.
Automatic  weight computation is a well-studied topic (for examples ~\citet{10.1145/2766952,BBW:2011,0.1145/2010324.1964968}) but typically requires solving an optimization problem
that itself relies on a volumetric discretization. 
This can be avoided by using stochastic methods~\cite{Sawhney:2020:MCG} but do not yet support the jump boundary conditions we require for our problem.

%All that remains for the deformation map is to compute blending weights. Our choice of the weighting function is guided by the simple idea that that for a given material point its weight should be highest to whichever surfaces it is closest. This idea lends itself to a simple distance-based weighting method. The first step in this process is to compute \textit{distance weights}. For a given point $\mathbf{X}$ and a set of $n$ we wish to compute a set of distance weights to each surface $\mathbf{\theta}(\mathbf{X}) = \left(\theta_1, \dots, \theta_i, \dots, \theta_n \right)$.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/raycasting_quadrature}
    \caption{Figure showing how raycasting quadrature works (top), convergence plot for volume integration (bottom}
    \label{fig:raycasting}
\end{figure}
